---
title: "hw4"
author: "Edwin Rivas Meraz"
date: "2/17/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(lattice)
library(tidyr)
source('apa.s')
```

# 4 Qian
```{r}
apa.dat %>%
  filter(tp > 30) -> pg30

apa.dat %>%
  filter(tp < 30) -> pl30

hist(pg30$apa)
hist(pl30$apa)

```

```{r}
pg30 %>%
  pull(apa) -> apag30

pl30 %>%
  pull(apa) -> apal30

qqapa <- qqplot(x = apag30, y = apal30, plot.it = FALSE)


ggplot(as.data.frame(qqapa), aes(x = x, y = y)) + 
  geom_point() + 
  geom_abline(intercept = 0, slope = 1) + 
  coord_fixed(ratio = 1, 
              xlim = range(c(qqapa$x, qqapa$y)), 
              ylim = range(c(qqapa$x, qqapa$y))) +
  xlab('TP > 30') +
  ylab('TP < 30') +
  ggtitle('APA Distributions')

```

## b

The distributions are multiplicative indicating they differ in location and spread


## c
```{r}
t.test(x = apag30, y = apal30, var.equal = T)

```


# 3.1 Helsel
```{r}
gd <- data.frame('granodiorite' = c(6.0, 0.5, 0.4, 0.7, 0.8, 6.0, 5.0, 0.6, 1.2, 0.3, 0.2, 0.5, 0.5, 10, 0.2, 0.2, 1.7, 3.0))
gdsort <- sort(gd$granodiorite) #ascending order
gdsort

hist(gdsort)

#nonparametric n<20
#confidence interval 95%
#quantile 0.5
a <- 0.05
1-a
a/2 #x' = 4
n.gd <- 18 #n
Rl <- 4+1 #x'+1
Ru <- n.gd-4 #n-x'


#at n=18
gdsort[Rl]
gdsort[Ru]

lowgd <- gdsort[Rl]+0.025*(gdsort[Rl]-gdsort[Rl])
uppgd <- gdsort[Ru]+ 0.025*(gdsort[Ru]-gdsort[Ru])

print(paste(lowgd, "to", uppgd, "mg/L"))

#parametric
log.gd <- log(gdsort)

ybar <- mean(log.gd)
sd.gd <- sd(log.gd)^2
n.gd <- 18


hist(log.gd) #not normally distributed

lowgd1 <- exp(ybar-2.110*sqrt(sd.gd/n.gd)) #2.110 from t table of n-1
uppgd1 <- exp(ybar+2.110*sqrt(sd.gd/n.gd))

print(paste(lowgd1, "to", uppgd1, "mg/L"))
```

The nonparametric interval estimate for the median is between 0.5 and 0.8

The parametric interval estimate for the median is between 0.51 and 1.80

It is likely more appropriate to utilize a nonparametric interval for this dataset due to the lack of normal or lognormal distribution 

# 3.4
```{r}
streamflow <- data.frame('year' = c(1941:1960), 'flow.cfs' = c(369, 683, 923, 1193, 413, 1025, 894, 859, 1157, 524, 327, 574, 762, 578, 379, 375, 581, 581, 530, 929))

flow.cfs <- streamflow$flow.cfs

hist(flow.cfs)
mean.flow <- mean(flow.cfs)
flowsort <- sort(flow.cfs)
median.flow <- median(flowsort)


#median
#n = 20
#quantile = 0.5
#x'=5 from table of binomial distribution
a <- 0.05
1-a
a/2 #x' = 5
n.flow <- 20 #n
Rlf <- 5+1 #x'+1
Ruf <- n.flow-5 #n-x'

lowflow1<- flowsort[Rlf]+0.025*(flowsort[Rlf]-flowsort[Rlf])
uppflow1<- flowsort[Ruf]+ 0.025*(flowsort[Ruf]-flowsort[Ruf])
print(paste('Median of', median.flow, 'from', lowflow1, "to", uppflow1, "mg/L"))

#mean
sd.flow <- sd(flow.cfs)

lowflow <- mean.flow-2.093*sqrt(sd(flow.cfs)^2/n.flow) #lower bound, 2.093 from t table 
uppflow <- mean.flow+2.093*sqrt(sd(flow.cfs)^2/n.flow) #upper bound

int <- mean.flow-lowflow

print(paste("Mean of", mean.flow, "+/-", int, "from", lowflow, "to", uppflow, "cfs"))

```

